### 2025-03-02 paper/main.tex
tweak

\section*{\raggedright
A new formula for the area of a triangle:
Useless, but explicitly in Deep Sets and map--reduce form\footnote{%
The authors thank Alexander Novara (NYU), Ben Wandelt (Sorbonne), and Kaze Wong (Flatiron) for valuable discussions.}}

>>>>

\section*{\raggedright
A new formula for the area of a triangle:
Useless, but explicitly in Deep Sets and map--reduce form\footnote{%
The authors thank Alexander Novara (NYU), Ben Wandelt (Sorbonne), and Kaze Wong (JHU) for valuable discussions.}}
